---
title: "Theme Gallery"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Showcase of bundled themes in **rstudiothemes**.

<!--- pkgdown only ---->

<style>
  .like_h {
    font-size: 1.5rem;
    font-weight: 800;
    font-family: 'Inter Tight';
    text-shadow: 0 0 6px black;
    color: white;
  }

</style>

```{r setup, echo=FALSE}
library(rstudiothemes)

themes <- list_rstudiothemes(list_installed = FALSE)

png_name <- paste0(gsub(" ", "", tolower(themes)))

pths <- file.path("screenshots", paste0(png_name, ".png"))
```

<div class="container py-4">
<!-- Dropdown -->

```{r dropdown, echo=FALSE, results='asis'}
# Create drowndown
cat(paste0(
  "<select id=\"carouselSelector\" class=\"form-select mb-3\" ",
  "style=\"max-width: 300px;\">"
))
cat()
for (i in seq_along(themes)) {
  cat(paste0("<option value=\"", png_name[i], "\">", themes[i], "</option>\n"))
}
cat("</select>")
```

<!-- Carousel -->
<div id="myCarousel" class="carousel slide carousel-fade" data-bs-ride="carousel">

<div class="carousel-inner">

```{r create_themes, echo=FALSE, results='asis'}
for (i in seq_along(themes)) {
  if (i == 1) {
    cat(c(paste0(
      "\n<div class=\"carousel-item active\" id=\"",
      png_name[i], "\">"
    )), sep = "\n")
  } else {
    cat(c(paste0(
      "\n<div class=\"carousel-item\" id=\"",
      png_name[i], "\">"
    )), sep = "\n")
  }

  cat(c(paste0(
    "<img src=\"", pths[i], "\" class=\"d-block w-100\" alt=\"\">"
  )), sep = "\n")

  cat("<div class=\"carousel-caption d-block pb-0\">", sep = "\n")
  cat(c(paste0("<p class=\"like_h\">", themes[i], "</p>")))
  cat("</div>\n</div>\n", sep = "\n")
}
```
</div>
<!-- Controls -->
<button class="carousel-control-prev" type="button" data-bs-target="#myCarousel" data-bs-slide="prev">
<span class="carousel-control-prev-icon"></span>
</button>
<button class="carousel-control-next" type="button" data-bs-target="#myCarousel" data-bs-slide="next">
<span class="carousel-control-next-icon"></span>
</button>
</div>
</div>

<script>
  const carouselElement = document.getElementById('myCarousel');
  const carousel = bootstrap.Carousel.getOrCreateInstance(carouselElement);
  const selector = document.getElementById('carouselSelector');

  // Build an array of slide IDs in order
  const slideIds = Array.from(
    carouselElement.querySelectorAll('.carousel-item')
  ).map(item => item.id);

  // Dropdown > go to slide
  selector.addEventListener('change', () => {
    const id = selector.value;
    const index = slideIds.indexOf(id);
    if (index !== -1) {
      carousel.to(index);
    }
  });

  // Carousel > update dropdown
  carouselElement.addEventListener('slid.bs.carousel', (e) => {
    selector.value = slideIds[e.to];
  });
</script>
