---
title: "Showcase"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Showcase of bundled themes in **rstudiothemes**.

We also distribute all our themes in a single `.zip` file at <https://dieghernan.github.io/rstudiothemes/dist/rstudiothemes.zip>. Unzip and install using the [RStudio IDE interface](https://support.posit.co/hc/en-us/articles/115011846747-Using-Themes-in-the-RStudio-IDE).

*Click the image to enlarge*
<!--- pkgdown only ---->

<style>

.lightbox-caption em{
  font-style: normal;
  font-size: 300%;
  font-weight: 800;
  font-family: 'Inter Tight';
  text-shadow: 0 0 10px black;
  color: white;
}
.lightbox-caption {
  position: absolute !important;
  top: 20%;
  right: 0;
  left: 0;
  z-index: 1;
  opacity:0.2;
}
.like_h {
  text-shadow: 0 0 8px black;
  opacity: 0.7;
  color: white;
}
</style>


```{r setup, echo=FALSE}
library(rstudiothemes)

themes <- list_rstudiothemes(list_installed = FALSE)

png_name <- paste0(gsub(" ", "", tolower(themes)))

pths <- file.path("screenshots", paste0(png_name, ".png"))

th_url <- file.path(
  "https://dieghernan.github.io/rstudiothemes/articles/",
  pths
)
```

<div class="row row-cols-1 row-cols-md-2 g-1">

```{r card_layout, echo=FALSE, results='asis'}
for (i in seq_along(themes)) {
  cat("<div class=\"col\">")
  cat("<div class=\"card bg-dark text-white\">")
  cat(c(paste0(
    "<img src=\"", pths[i], "\" class=\"card-img\" alt=\"\">"
  )), sep = "\n")

  cat(
    paste0(
      "<div class=\"card-img-overlay\" data-toggle=\"lightbox\" ",
      "data-gallery=\"rstudiothemes\" data-src=\"",
      th_url[i], "\" data-caption=\"", themes[i], "\" >"
    )
  )
  cat(c(paste0("<h5 class=\"like_h\">", themes[i], "</h5>")))
  cat("</div>")
  cat("</div>")
  cat("</div>")
}
```


</div>


<script src="https://cdn.jsdelivr.net/npm/bs5-lightbox@1.8.5/dist/index.bundle.min.js"></script>
